Bus lines, multilines approach

### 2022-03-29 multiple_lines/notes/latex/Notes_trajet.tex
Multiline latex change

Suppose that we possess two $n$-length vectors $\mathbf{x}_\text{in} = (x^\text{in}_i)$ and $\mathbf{y}_\text{out} = (y^\text{out}_i)$, representing respectively the flow entering the network at stop $i$ and going out of the network at stop $i$.

>>>>

A \emph{flow matrix} $\mathbf{N} = (n_{ij})$. Suppose that we possess two $n$-length vectors $\mathbf{x}_\text{in} = (x^\text{in}_i)$ and $\mathbf{y}_\text{out} = (y^\text{out}_i)$, representing respectively the flow entering a line at stop $i$ and going out of the line at stop $i$.
